---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  dpi=200,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ElectionsLATAM

 <!-- Database Agnostic Package to Generate and Process 'SQL' Queries in R. -->

 Allows the user to generate and execute select, insert, update and delete 'SQL' queries the underlying database without having to explicitly write 'SQL' code. 


| Release | Usage | Development |
|:--------|:------|:------------|
|| [![minimal R version](https://img.shields.io/badge/R%3E%3D-4.0.0-blue.svg)](https://cran.r-project.org/) | [![R-CMD-check](https://github.com/rOpenStats/ElectionsLATAM/workflows/R-CMD-check/badge.svg)](https://github.com/rOpenStats/ElectionsLATAM/actions)|
| [![CRAN](http://www.r-pkg.org/badges/version/ElectionsLATAM)](https://cran.r-project.org/package=ElectionsLATAM) | | [![codecov](https://codecov.io/gh/rOpenStats/ElectionsLATAM/branch/master/graph/badge.svg)](https://app.codecov.io/gh/rOpenStats/ElectionsLATAM) |
|||[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)|

# How to get started
```R
# Not yet published in CRAN
# install.packages("ElectionsLATAM")
```

# How to get started (Development version)

Install the R package using the following commands on the R console:

```R
devtools::install_github("rOpenStats/ElectionsLATAM", build_opts = NULL)
```

# A simple example 

To get started execute the following commands:

```{r, load}
# 0.  Load libraries
library(ElectionsLATAM)
library(dplyr)
library(readr)
```

```{r, costa-rica}

# 1.  Costa Rica
costa.rica.ein.path <- file.path(getPackageDir(), "costa-rica")
ecological.inference.calvo <- EcologicalInferenceStrategyCalvoEtAl$new()
costa.rica.ein <-
    EcologicalInferenceProcessor$new(
      ecological.inference.strategy = ecological.inference.calvo,
      election.name = "2022-costa-rica-general-ballotage-n4",
      scenario = "final",
      data.input.path = costa.rica.ein.path,
      input.file = "2021-generales_pivot_candidatos_n4.csv",
      location.fields = c("id_unidad"),
      votes.field = "votos",
      #potential.votes.field = "habilitados",
      ignore.fields = "habilitados",
      col.types = cols(
        .default = col_number(),
        id_unidad = col_character()
      )
    )
dummy <- costa.rica.ein$loadInputPivotCandidatos()
costa.rica.ein$output.election <- readr::read_delim(
    #ballotage.processor$pivot.filepath,
    file.path(costa.rica.ein.path,
              paste("2022-ballotage_pivot_candidatos_n4.csv", sep = "_")),
    delim = ";",
    col_types = cols(
      .default = col_double(),
      id_unidad = col_character()
    )
  )
costa.rica.ein$runScenario(include.blancos = TRUE, include.ausentes = TRUE,
                           max.potential.votes.rel.dif = 0.32)
costa.rica.test.path <- file.path(tempdir(), "test","costa-rica")
costa.rica.ein$exportBetab(output.folder = costa.rica.test.path, overwrite = TRUE)
dummy <- costa.rica.ein$generateOutputJSON(costa.rica.test.path,
                                           filename = "balotaje_n4_ei.json")

costa.rica.ein$makeSankeyDiagram(output.path = costa.rica.test.path)
# Saving output table for reproducibility
#  write_rds(costa.rica.ein$output.table, file.path(costa.rica.ein.path, "ein_2021_general_2022_ballotage.rds"))
```


# Troubleshooting


Please note that the 'ElectionsLATAM' project is released with a [Contributor Code of Conduct](https://github.com/rOpenStats/ElectionsLATAM/blob/master/CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.


